Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way

### 2025-04-16 paper/ms.tex
Fix citation

\edit1{The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}. This is thought to arise from flaring associated with radial migration \citep{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}. Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}

>>>>

\edit1{The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}. This is thought to arise from \edit2{inside-out formation} \citep[\edit2{which predict and claim a negative age gradient at high altitude}]{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}. Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}
